Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
2.3 OpenMP

In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure gets back to the single-threaded execution mode~\cite{Wu2014}.

@@

In the above example, the for loop is executed in parallel \textcolor{blue}{Como? Cada posicao do array eh executada em um nucleo diferente? Não é garantido que use. Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}. Each iteration of the loop is executed in a separated thread. \textcolor{red}{Each thread may use an idle processor}.

There is also a way to specify critical regions, which is a block of code that is guaranteed to be execute by a single thread at a time. To create a critical region   the directive ``\#pragma omp critical'' should be used.
%----------------------------------------------
\subsection{Solving Optimization Problems with Vz}
\label{Optimization-with-Vz}
%----------------------------------------------

>>>>

In particular, OpenMP uses the fork-join model of parallel execution ~\cite{OpenMP1998}. The main thread executes the sequential parts of the program; if a parallel region is encountered, then it forks a team of worker threads. After the parallel region finishes ({\it i.e.}, the API waits until all threads terminate), then the main procedure returns to the single-threaded execution mode~\cite{Wu2014}.

@@

In the above example, the for loop is executed in parallel \textcolor{blue}{Como? Cada posicao do array eh executada em um nucleo diferente? Não é garantido que use. Isto depende da afinidade do processo com os cores e tambem da quantidade de cores existentes.}. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor.

There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\#pragma omp critical'' directive should be used.
%----------------------------------------------
\subsection{Solving Optimization Problems with Vz}
\label{Optimization-with-Vz}
%----------------------------------------------
